Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-02-28 ms.tex
numbers

The 1016 pixel by 1016 pixel WISE single-exposure ``L1b'' images represent
the input data for our W1/W2 coadds. Specifically, for each L1b frameset, we 
make use of the per-band \verb|-int-|, \verb|-msk-| and \verb|-unc-| images, 
which respectively give the measured sky intensity and associated per-pixel 
bitmask values and uncertainty estimates. We have obtained a local copy of 
these files for every W1 and W2 frameset, including those from the AllWISE 
release ($\sim$2.9M framesets) and first-year NEOWISER release ($\sim$2.5M 
framesets). In total we have analyzed $\sim$5.4M framesets in each of W1 and 
W2, corresponding to a total of $\sim$32M L1b image files and $\sim$71TB of 
pixel data.

>>>>

The 1016 pixel by 1016 pixel WISE single-exposure ``L1b'' images represent
the input data for our W1/W2 coadds. Specifically, for each L1b frameset, we 
make use of the per-band \verb|-int-|, \verb|-msk-| and \verb|-unc-| images, 
which respectively give the measured sky intensity and associated per-pixel 
bitmask values and uncertainty estimates. We have obtained a local copy of 
these files for every W1 and W2 frameset, including those from the AllWISE 
release ($\sim$2.8M framesets) and first-year NEOWISER release ($\sim$2.5M 
framesets). In all we have analyzed $\sim$5.3M framesets in each of W1 and 
W2, corresponding to a total of $\sim$32M L1b image files, $\sim$71TB of 
input image data and $\sim$33$\times$10$^{12}$ pixels.
